### 2018-12-09 writing/thesis/chapters/scenarios.tex
Add CJ-detonation wave scenario.

\subsection{The first Stokes Problem}
\cite{dumbser2010arbitrary}
\subsection{Taylor-Green Vortex}
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) cos(y) \\
- \cos(x) sin(y) 
    \end{pmatrix} \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
  \end{split}
\end{align}
\todo{Constants!}
$C = 100/\gamma$ \cite{dumbser2016high}

@@

>>>>

\subsection{The first Stokes Problem}
\todo{Do I actually want to include this? Bit boring scenario}
\cite{dumbser2010arbitrary}
\subsection{Taylor-Green Vortex}
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) cos(y) \\
- \cos(x) sin(y) 
    \end{pmatrix} \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
  \end{split}
\end{align}
\todo{Constants!}
$C = 100/\gamma$ \cite{dumbser2016high}

@@

\subsection{Radialsymmetric CJ Detonation Wave}
We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
This scenario for the reactive Euler-equations is set up in a 2D box of size $[-0.5, 0.5] \times [-0.5, 0.5]$.
Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
Let $\alpha =  \operatorname{atan2}(y,x)$ be the angle in polar coordinates.
We use the initial conditions
\begin{align}
  \begin{split}
  \Qrho_u &= 0.887565\\
  \Qv_u &= -0.577350
  \begin{pmatrix}
     \cos (\alpha)\\
     \sin (\alpha)
  \end{pmatrix} \\
  \pressure_u &= 0.191709 \\
  \QZZ_u &= 1
  \end{split}
\intertext{for the burnt gas and}
\begin{split}
  \Qrho_b &= 1.4\\
  \Qv_b &= 0\\
  \pressure_b &= 1 \\
  \QZZ_b &= 0
  \end{split}
\end{align}
for the unburnt gas.
